\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=20mm]{geometry}

\usepackage{booktabs}
\usepackage{titlesec}
\usepackage{url}

\DeclareUrlCommand{\email}{\def\UrlLeft{http://}\def\UrlRight{\UrlLeft}\urlstyle{tt}}

\pagestyle{empty}
\linespread{1.15}

\titleformat{\section}{\LARGE\bfseries}{}{0em}{\thispagestyle{empty}}

\begin{document}

\vspace{-10mm}

\begin{center}
{\Huge\bfseries Pham Binh An}\\[3mm]
\small
phambinhanctb2004@gmail.com \textbullet\ (+84) 036 956 5170 \textbullet\ github.com/brianhuster
\end{center}

\hrule width \hsize \hskip .1em \hrule width \hsize height 0.5pt

\vspace{5mm}

\section{Education}
\begin{tabular}{p{2.5cm}p{13cm}}
\textbf{2022 -- 2026} & \textbf{Hanoi University of Science and Technology (HUST)}\\
& Faculty of Information and Communication Technology\\
& \textbf{Major:} Educational Technology (Expected Graduation)\\
\end{tabular}

\vspace{4mm}

\section{Skills}
\begin{tabular}{p{2.5cm}p{13cm}}
\textbf{Programming} & Python, JavaScript, Lua, Bash, Go\\
\textbf{Backend} & Node.js, Express.js, FastAPI (learning)\\
\textbf{Database} & MySQL, MongoDB\\
\textbf{Tools} & Git, Docker, Vim, Linux\\
\textbf{Open Source} & Contributor to Neovim and Vim\\
\textbf{Languages} & Vietnamese (Native), English (TOEIC 800), Japanese (N4, learning N3)\\
\end{tabular}

\vspace{4mm}

\section{Achievements}
\begin{itemize}
    \setlength\itemsep{6pt}
    \item \textbf{728} GitHub stars, \textbf{91} repositories, \textbf{14} followers
    \item \textbf{University Scholarship} (2022--2024): Semesters 20221, 20222, 20232
    \item \textbf{Consolation Prize} -- Student Creative Ideas Challenge 2024, HUST (Smart glasses project for visually impaired people)
\end{itemize}

\vspace{4mm}

\section{Experience}
\begin{tabular}{p{2.5cm}p{13cm}}
\textbf{Sep 2023} & \textbf{Global Project Based Learning} -- HUST\\
& Collaborated with Vietnamese and Japanese students on an IoT medicine delivery robot for smart hospitals. Developed teamwork, cross-cultural communication, and problem-solving skills.\\
\end{tabular}

\vspace{4mm}

\section{Selected Projects}
\vspace{2mm}

\textbf{live-preview.nvim} (Lua) -- \url{github.com/brianhuster/live-preview.nvim}\\
\textit{Neovim plugin for live previewing Markdown, HTML, AsciiDoc, SVG in web browser. HTTP and WebSocket servers implemented in Lua based on Libuv TCP connections.}\\
\textbf{360 stars, 24 forks, 23 contributors}\\[3mm]

\textbf{ollama-acp} (Python) -- \url{github.com/brianhuster/ollama-acp}\\
CLI tool connecting to Ollama server via Agent Client Protocol (ACP). Built with Python, subprocess, and asyncio. MIT License.\\[3mm]

\textbf{nvcat} (Go) -- \url{github.com/brianhuster/nvcat}\\
\`cat\` with syntax highlighting powered by Neovim. 37 stars, 4 forks.\\[3mm]

\textbf{unnest.nvim} (Lua) -- \url{github.com/brianhuster/unnest.nvim}\\
Neovim plugin for handling nested terminal sessions without losing context. 95 stars, 2 forks.\\[3mm]

\textbf{Gamehub} (Node.js) -- \url{github.com/brianhuster/Gamehub}\\
Full-stack game hub website with admin panel. Tech: Node.js, Express.js, MySQL, EJS.

\vspace{4mm}

\section{Extracurricular Activities}
\begin{tabular}{p{2.5cm}p{13cm}}
2023--present & \textbf{EGG Club} -- Educational Committee\\
Jul 2023 & \textbf{STEM \& E-Learning} -- Training organizer for teachers in Quang Binh province\\
Apr 2024 & \textbf{Tech Club Championship} -- Organizing committee member\\
\end{tabular}

\vfill
\hfill \url{github.com/brianhuster}

\end{document}
